\section{Literature Review}

A lot of research has already been done on the differences between client-side rendering and server-side rendering within web applications. In most studies, the focus is on performance in terms of speed and user experience. Nordström and Dixelius (2023) demonstrate that SSR can deliver better load performance than CSR for larger and more complex web pages, while for smaller pages the difference is minimal. Clapton et al. (2025) provide quantitative evidence, showing that SSR significantly outperforms CSR on metrics such as Time To Interactive (TTI) with a mean reduction of 62.3\% and Largest Contentful Paint (LCP) with a mean reduction of 58.7\%, particularly under increased data loads. Conversely, CSR exhibits better First Contentful Paint (FCP) and Speed Index (SI) performance for smaller datasets.

Ojala (2025) describes that SSR offers advantages in terms of search engine optimization (SEO) and initial load time. This is further supported by Gaddam (2025), who reports that SSR reduces page load times by an average of 37.5\% compared to CSR, with FCP achieved in 1.89 seconds versus 3.02 seconds for CSR, and TTI improvements averaging 42.3\%. From an SEO perspective, Google's rendering engine strongly favors server-rendered content, with SSR implementations receiving complete indexing at rates 3.4 times higher than client-rendered equivalents. At the same time, processing JavaScript pages takes significantly longer, with an average processing time of 5-7 days compared to 48 hours for server-rendered content. SSR also delivers tangible business benefits, with implementations experiencing 27.8\% more organic traffic growth over six months compared to CSR. However, Ojala (2025) also notes that SSR introduces extra complexity in the development process, for example through server load and the use of hydration mechanisms.

What stands out in these studies is that performance is almost always interpreted as speed or user experience, and less often as efficient use of resources. In some studies, CPU and memory usage are also examined. Gaddam (2025) reports that SSR on average leads to significantly lower CPU and memory load during the render phase, particularly on client devices. Specifically, SSR implementations demonstrate 28.7\% reduction in memory consumption and 31.2\% reduction in CPU usage. This is explained by the fact that a larger part of the processing takes place on the server, meaning the client needs to execute less JavaScript. Clapton et al. (2025) analyze the use of the JavaScript Heap across different data sizes and show that with larger datasets (ranging from 498 KB to 26 MB), the client-side load with CSR increases significantly compared to SSR. This suggests that the choice of render strategy not only affects speed, but also the computational load on the user's device.

When examining energy consumption aspects of web applications, it becomes apparent that this topic has received limited direct attention in relation to rendering strategies. Thiagarajan et al. (2012) conducted pioneering research with a hardware-based measurement setup measuring the precise energy consumption of mobile browsers rendering web pages. Their work demonstrated that JavaScript and CSS processing in the browser have a significant influence on the energy consumption of mobile devices. They discovered that downloading and parsing cascading stylesheets and JavaScript consumes a substantial fraction of the total energy needed to render a page. Additionally, they found that complex JavaScript and CSS can be as expensive to render as images, and that dynamic JavaScript requests (XMLHttpRequest) can greatly increase the cost of rendering pages. Through optimization of popular websites, Thiagarajan et al. achieved energy savings of 29\% on the Wikipedia mobile site by modifying JavaScript execution without affecting user experience.

Recent studies, such as Kalliola and Vepsäläinen (2025), indicate that measuring energy consumption of web applications is complex and an active research area. They note that while CPU usage can serve as a useful proxy indicator for energy consumption, existing online ``energy calculators'' often give inaccurate or inconsistent results and fail to acknowledge important optimization techniques such as lazy rendering. Their findings recommend using CPU-based measurement methods for estimating web energy consumption. The broader context is significant: the ICT industry is estimated to consume 7-10\% of the world's energy, with approximately 70\% of this consumption occurring during the use phase. The web, being the largest available application platform globally, represents a substantial portion of this energy consumption.

What stands out in the existing literature is that resource usage and energy efficiency rarely form the primary research objective in rendering strategy comparisons. CPU and memory measurements are often included as supporting metrics in performance analyses, but not as central evaluation criteria. Furthermore, the connection between rendering strategies and energy consumption has been underexplored, with most energy-focused research predating modern rendering frameworks and optimization techniques.

Based on this literature, it can be concluded that SSR and CSR have been extensively compared in terms of speed, user experience, and SEO. It has also been shown that render strategies influence CPU and memory usage on client devices and can affect battery consumption during rendering. However, there appears to be limited research that explicitly compares SSR and CSR with resource efficiency and energy consumption as the primary focus, and specifically within a mobile context. This forms the motivation for the current research, in which the emphasis shifts from ``performance as speed'' to ``performance as resource efficiency''.
