\section{Research Design \& Methods}

To investigate the effect of server-side rendering (SSR) and client-side rendering (CSR) on mobile-side resource efficiency, a controlled benchmark was designed around one comparable web application implemented in two rendering variants. The goal was not to compare different frameworks or unrelated architectures, but to isolate where the main computation took place while keeping the application stack, interface, and data model as stable as possible.

The study started with a literature review to position the work within existing SSR/CSR performance research. This was followed by a problem analysis in which performance was treated not only as speed, but also as resource efficiency on a mobile device. On that basis, a prototype was built in Next.js using two routes: an SSR route and a CSR route. Both routes rendered the same storefront interface, used the same underlying mock inventory model, and exposed the same query controls for scenario, search term, category, sort order, and pagination.

The intentional difference between the two variants was where the expensive data preparation happened. In the SSR variant, the server read the selected scenario, loaded the inventory, and performed filtering, sorting, pagination, product decoration, and summary construction before returning the rendered page. In the CSR variant, the browser first loaded the page shell, then fetched the raw inventory from an API endpoint after hydration, after which the client performed the equivalent filtering, sorting, pagination, decoration, and summary computation locally. This design made the final UI state comparable while shifting the main computational burden between server and client.

Three dataset scenarios were implemented in the prototype. The \textit{static} scenario contained 72 records and represented a small editorial catalogue. The \textit{dynamic} scenario contained 6{,}000 records and represented a medium-sized live catalogue. The \textit{massive} scenario contained 24{,}000 records and represented a larger marketplace-style stress case. Combined with the two rendering strategies, this yielded six benchmark conditions: SSR-static, SSR-dynamic, SSR-massive, CSR-static, CSR-dynamic, and CSR-massive.

The experiment was orchestrated through shell and analysis scripts in the repository. For each benchmark session, the Next.js application was built and started locally, exposed to the Android device through \texttt{adb reverse}, and exercised through an automated Puppeteer-based scenario over the Chrome DevTools Protocol. Runs were randomised across all conditions to reduce ordering effects. The final wireless benchmark used 10 repetitions per condition, resulting in 60 total runs. Between runs, Chrome was force-stopped, the device returned to a neutral state, and a cooldown period of 45 seconds was applied.

Measurements were collected on a Samsung Galaxy A53 (SM-A536B). Browser metrics for the initial page load included time to first byte (TTFB), first contentful paint (FCP), largest contentful paint (LCP), total blocking time (TBT), cumulative layout shift (CLS), and transfer size. Direct energy was estimated from repeated battery polling via \texttt{adb dumpsys battery}, integrating absolute current and voltage over time. In the final wireless dataset, battery polling occurred every 0.25 seconds. Device temperature was logged before each run to monitor thermal stability, and screen brightness was fixed to reduce measurement variation.

An important methodological correction was made during the study. Earlier USB-connected runs were useful for validating the tooling and general collection stability, but USB power could contaminate direct battery-current measurements. For that reason, the final energy analysis is based primarily on the battery-powered wireless run. This adjustment should be understood as a measurement limitation that was identified and addressed, rather than as a failure of the study design.

The resulting run data were processed with repository analysis scripts that extracted per-run energy metrics, aggregated browser measurements, and generated descriptive statistics. Because the final wireless dataset contained visible energy outliers, medians and interquartile ranges were treated as the primary descriptive statistics. Condition pairs were compared with a two-sided Mann-Whitney U test ($\alpha = 0.05$), and Bonferroni correction was applied to account for multiple comparisons.

\begin{table}[htbp]
\centering
\caption{Method overview used in this study.}
\label{tab:method-overview-2026}
{\small
\setlength{\tabcolsep}{4pt}
\begin{tabularx}{\linewidth}{@{}>{\RaggedRight\arraybackslash}p{2.3cm}>{\RaggedRight\arraybackslash}p{2.6cm}>{\RaggedRight\arraybackslash}p{1.9cm}>{\RaggedRight\arraybackslash}X@{}}
\toprule
\tablehead{Phase} & \tablehead{Method} & \tablehead{Type} & \tablehead{Purpose} \\
\midrule
Orientation & Literature study & Library & Establishing the known SSR and CSR performance landscape \\
Orientation & Best-practices analysis & Library & Identifying practical optimization factors for fair implementation \\
Analysis & Problem analysis & Field & Defining performance as resource efficiency instead of only speed \\
Analysis & Domain modelling & Field & Mapping how server-side and client-side computation differ within one shared stack \\
Design & Prototyping & Workshop & Building one storefront prototype with SSR and CSR variants across three dataset scenarios \\
Test phase & Instrumented benchmark & Lab & Measuring battery-derived energy, load metrics, transfer size, and thermal stability under controlled conditions \\
Test phase & Repeated runs & Showroom & Comparing six conditions directly across randomised repeated runs on the same device \\
Analysis & Statistical analysis & Field & Computing medians, IQR, effect size, and non-parametric significance tests \\
Validation & Peer review & Showroom & Checking method quality and interpretation consistency \\
\bottomrule
\end{tabularx}
}
\end{table}
