\section{Results}

% Placeholder figure labels if the generated analysis plots are added later:
% fig:wireless-energy-distributions
% fig:wireless-browser-distributions

The results reported in this section are based on the corrected battery-powered wireless benchmark run. This final benchmark contained 60 runs in total: 10 repetitions for each combination of rendering strategy (SSR and CSR) and scenario (\textit{static}, \textit{dynamic}, and \textit{massive}). All 60 runs were battery-valid, all 60 runs produced browser metrics through the Chrome DevTools Protocol path, and the recorded device temperature remained between 25.1 and 26.1\,$^\circ$C throughout the session. Because the energy measurements contained several high-value observations, especially in some CSR conditions, medians and interquartile ranges (IQR) are treated as the primary descriptive statistics.

\begin{table}[htbp]
\centering
\caption{Energy results for the corrected wireless benchmark. Medians are reported with IQR in parentheses.}
\label{tab:wireless-energy-summary}
{\small
\setlength{\tabcolsep}{4pt}
\begin{tabularx}{\linewidth}{@{}l l >{\RaggedRight\arraybackslash}X >{\RaggedRight\arraybackslash}X c@{}}
\toprule
\tablehead{Scenario} & \tablehead{Metric} & \tablehead{SSR median (IQR)} & \tablehead{CSR median (IQR)} & \tablehead{$p$} \\
\midrule
dynamic & Total energy (mJ) & 6372.2 (1684.6) & 7040.3 (1281.9) & 0.2730 \\
dynamic & Average power (mW) & 836.5 (206.8) & 773.6 (91.6) & 0.2413 \\
massive & Total energy (mJ) & 5769.5 (401.8) & 9047.8 (18662.8) & 0.0008 \\
massive & Average power (mW) & 768.7 (73.8) & 1044.1 (2242.0) & 0.0211 \\
static & Total energy (mJ) & 5742.9 (378.8) & 7960.1 (2159.5) & 0.0013 \\
static & Average power (mW) & 764.0 (30.2) & 855.3 (232.9) & 0.0028 \\
\bottomrule
\end{tabularx}
}
\end{table}

Table~\ref{tab:wireless-energy-summary} shows that SSR yielded lower median total energy in all three scenarios. In the \textit{dynamic} scenario, the difference remained directional rather than conclusive, with a median of 6372.2~mJ for SSR and 7040.3~mJ for CSR ($p = 0.2730$). In the \textit{massive} scenario, the difference was larger: SSR reached a median of 5769.5~mJ compared with 9047.8~mJ for CSR ($p = 0.0008$). The \textit{static} scenario showed a similar pattern, with SSR at 5742.9~mJ and CSR at 7960.1~mJ ($p = 0.0013$). Under the Bonferroni-corrected threshold reported by the analysis scripts ($\alpha = 0.0019$), the total energy differences in the \textit{massive} and \textit{static} scenarios remained supported, whereas the \textit{dynamic} difference did not.

The spread of the energy distributions was not uniform across conditions. The SSR distributions were comparatively compact in the \textit{static} and \textit{massive} scenarios, with IQR values of 378.8~mJ and 401.8~mJ respectively. By contrast, CSR showed notably wider dispersion, especially in the \textit{massive} scenario, where the IQR reached 18662.8~mJ. This wide spread reflects several high-energy CSR runs and reinforces the decision to interpret the corrected wireless benchmark primarily through medians rather than arithmetic means.

\begin{table}[htbp]
\centering
\caption{Selected browser and client-resource metrics for the corrected wireless benchmark. Medians are reported with IQR in parentheses.}
\label{tab:wireless-browser-summary}
{\small
\setlength{\tabcolsep}{4pt}
\begin{tabularx}{\linewidth}{@{}l l >{\RaggedRight\arraybackslash}X >{\RaggedRight\arraybackslash}X c@{}}
\toprule
\tablehead{Scenario} & \tablehead{Metric} & \tablehead{SSR median (IQR)} & \tablehead{CSR median (IQR)} & \tablehead{$p$} \\
\midrule
dynamic & LCP (ms) & 3302.0 (16.0) & 3270.0 (25.0) & 0.0010 \\
dynamic & TTFB (ms) & 31.2 (76.8) & 22.1 (46.0) & 0.1859 \\
dynamic & Transfer size (KB) & 7.1 (0.0) & 3.9 (0.0) & $< 0.0001$ \\
dynamic & JS heap peak (MB) & 9.5 (0.0) & 9.5 (0.0) & 1.0000 \\
massive & LCP (ms) & 3296.0 (16.0) & 3274.0 (26.0) & 0.0532 \\
massive & TTFB (ms) & 67.8 (83.8) & 21.9 (139.4) & 0.1405 \\
massive & Transfer size (KB) & 7.1 (0.0) & 3.9 (0.0) & $< 0.0001$ \\
massive & JS heap peak (MB) & 9.5 (0.0) & 13.6 (0.0) & $< 0.0001$ \\
static & LCP (ms) & 3292.0 (16.0) & 3290.0 (15.0) & 1.0000 \\
static & TTFB (ms) & 24.1 (17.6) & 80.7 (135.0) & 0.9698 \\
static & Transfer size (KB) & 7.2 (0.0) & 3.9 (0.0) & $< 0.0001$ \\
static & JS heap peak (MB) & 9.5 (0.0) & 9.5 (0.0) & 1.0000 \\
\bottomrule
\end{tabularx}
}
\end{table}

The browser-facing metrics were more mixed than the energy results, as shown in Table~\ref{tab:wireless-browser-summary}. In the \textit{dynamic} scenario, CSR achieved lower median LCP and FCP values than SSR (3270.0~ms versus 3302.0~ms for both metrics, $p = 0.0010$) and also a lower median TTFB (22.1~ms versus 31.2~ms, $p = 0.1859$). In the \textit{massive} scenario, CSR again showed lower median LCP and FCP values (3274.0~ms versus 3296.0~ms, $p = 0.0532$) and a lower median TTFB (21.9~ms versus 67.8~ms, $p = 0.1405$), although these latency differences did not meet the corrected threshold. In the \textit{static} scenario, the latency picture changed: LCP and FCP were effectively equivalent between conditions, and the CSR TTFB distribution was substantially more variable, producing a higher median than SSR.

One result was consistent across all three scenarios: the measured navigation transfer size was lower for CSR than for SSR, with medians of approximately 3.9~KB for CSR and 7.1--7.2~KB for SSR ($p < 0.0001$ in every scenario). At the same time, Total Blocking Time and Cumulative Layout Shift remained at zero across all runs and therefore did not differentiate the conditions. The JavaScript heap metric also stayed equal at 9.5~MB in the \textit{dynamic} and \textit{static} scenarios. The clearest client-side resource difference appeared in the \textit{massive} scenario, where CSR reached a median heap peak of 13.6~MB compared with 9.5~MB for SSR ($p < 0.0001$). This result is consistent with the implementation difference in the prototype: CSR fetches raw inventory after hydration and performs the main data transformation step in the browser, whereas SSR performs that work before the page is delivered.
